Title

### 2023-06-07 main.tex
Merge pull my finger request

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in \fref{fig: circuit-pauli-1},
which is a special case of \fref{fig: circuit-pauli}
but with all details  explicitly shown.
In said figure, the ancilla state
of \eref{eq: state} can be taken to be
$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
and it is created on the ancilla qubits with the help of three rotations of angles:
\begin{subequations}
\begin{eqnarray}
\theta_0 &= &\arctan(\sqrt{k_{01}/k_{00}}) -
\arctan(\sqrt{k_{11}/k_{10}}),
\label{eq:angle1} \\ 
\theta_1 &= &2 \arccos(\sqrt{k_{00} +
k_{01}}),
\label{eq:angle2} \\
\theta_2 &= &\arctan(\sqrt{k_{01}/k_{00}}) +
\arctan(\sqrt{k_{11}/k_{10}}).
\label{eq:angle3}
\end{eqnarray}
\label{eq:angle}
\end{subequations}
\cpnote{Quisiera ver las ecuaciones sin la teheta despejada. Por ejemplo la de theta 1
es $\cos^2 (\theta_1/2) = k00 + k01$ bueno mas bonita, pero asi. Luego las de tehta0 y theta2 
quizá tambien sean sencillas. Las quiero ver!!!}
%\tbnote{Ah, ya entiendo. Las única forma que veo de escribirlas es:
%\begin{align*}
%\tan \theta_0 = \dfrac{\sqrt{k_{01}/k_{00}} - \sqrt{k_{11}/k_{10} }}{1+\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}} }} \\
%\tan \theta_2 = \dfrac{\sqrt{k_{01}/k_{00}} + \sqrt{k_{11}/k_{10} }}{1-\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}} }}
%\end{align*}
%No veo cómo escribir ecuaciones de las thetas no despejadas que sean sencillas.
%}

%\tbnote{Obteniendo el seno y coseno de estos ángulos tampoco se 
%consigue algo mucho mejor:
%\begin{align*}
%\cos \theta_0 = \dfrac{\sqrt{k_{00} k_{10}} + \sqrt{k_{01} k_{11}}}{\sqrt{(k_{00} + k_{01}) (k_{10} + k_{11})}} \\
%\sin \theta_0 =  \dfrac{\sqrt{k_{01} k_{10}} - \sqrt{k_{00} k_{11}}}{\sqrt{(k_{00} + k_{01}) (k_{10} + k_{11})}}  \\
%\cos \theta_2 = \sqrt{\dfrac{k_{00}k_{10}}{(k_{00}+k_{01})(k_{10}+k_{11})}} \left( -1 + \sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}} \right) \\
%\sin \theta_2 =  - \sqrt{\dfrac{k_{00}k_{10} + k_{01}k_{11} - 2 \sqrt{k_{00} k_{01} k_{10} k_{11}}}{(k_{00} + k_{01}) (k_{10} + k_{11})}} \left(\sqrt{\dfrac{k_{01}}{k_{00}}} + \sqrt{\dfrac{k_{11}}{k_{10}}} \right) \left(-1 + \sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}} \right)^{-1}
%\end{align*}
%Probé combinar estas cantidades de diferentes formas, pero ninguna se simplificaba.}

\tbnote{Creo que la mejor forma es la siguiente (nota:
intercambié los ángulos 0 y 1 en la imagen para que 1 y 2
sean los que van juntos y el 0 por separado, en lugar de que los juntos sean el 0 y 2) :}
\tbnote{of angles defined by the following equations:
\begin{align*}
\cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{00} + k_{01}}\\
\tan\left( \dfrac{\theta_1 + \theta_2}{2} \right) &= \sqrt{k_{01}/k_{00}} \\
\tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{11}/k_{10}}
\end{align*}
También podría quitar los factores de 2 que hay aquí y meter factores de 2 en los ángulos del circuito.
}

@@

We took a sample of one-qubit Pauli channels and
used the ibmq-lima quantum computer that IBM has available~\cite{Qiskit}
to simulate them. For each of these channels, we used quantum process
tomography~\cite{Qiskit, Chuang:1996} to obtain the 
operator $\xi_I$ corresponding to the implementation of the
circuit.  Then, we compared this operator with the ideal 
channel $\xi_T$  we
wanted to implement.

We took a sample of one-qubit Pauli channels
and evaluated their implementation on IBM's
ibmq-lima quantum computer~\cite{Qiskit},
as shown in \fref{fig:fids}. 
For each of the channels sampled, we used 
quantum process tomography~\cite{Qiskit, Chuang:1996} to obtain the 
operator $\xi_I$ corresponding to the implementation of the
circuit in the quantum computer. 
Then, we compared $\xi_I$ with the theoretical 
operator $\xi_T$ of the Pauli channel we wanted to implement.
To see how close the operators $\xi_I$ and 
$\xi_T$ are, we shall use the
diamond distance~\cite{Aharonov,Wilde}, which is defined by
\begin{equation}
||\xi_I - \xi_T ||_{\diamond}  = \max_{\rho} || (\xi_I \otimes I) \rho - (\xi_T \otimes I) \rho ||_1,
\end{equation}
with $I$ the identity map,
$|| \cdot ||_1$ the trace norm and the maximization
done over all density matrices $\rho$.
The calculation of this norm is done using the semi-definite program from reference \cite{Watrous}.
When the two channels are the same,
the diamond distance has a value of $0$, while in the case that the channels
are completely distingushable, the distance reaches its maximum value of $2$~\cite{Benenti}.
For the analysis done in \fref{fig:fids}, we define a sort of ``diamond fidelity'' as: 
\begin{equation}
f = 1 - \dfrac{1}{2} ||\varepsilon_I - \varepsilon_T ||_{\diamond},
\label{eq:diamond-fid}
\end{equation}
which ranges from $0$, when the channels have a maximum distance, to  $1$,
when they are exactly equal.

Finally, using the representation of Pauli channels in a tetrahedron as
in \eref{eq: conditions-tetrahedron},
we show in \fref{fig:fids} the diamond fidelity defined by \eref{eq:diamond-fid} for the channels
analyzed. 
We can see that channels close to the 
completely depolarizing
channel (that is close to the center of the tetrahedron)
have a high $f$, while those 
close to unitary channels have much lower $f$.
This means that channels closer to the 
completely depolarizing channel are simulated better on the quantum computers.
This is reasonable because quantum computers are prone to errors
that depolarize qubits, which isn't very problematic
when trying to simulate depolarization but it is 
when simulating unitary processes. \cpnote{Tambien creo qeu debemos comentar que nuestra 
simulación para operaciones unitarias no es optima, porque usamos un monton de compuertas 
y además operaciones doblemente controladas.}
\tbnote{Algo como: }
{\color{orange} Moreover, the algorithm of \fref{fig: circuit-pauli-1} is not optimal for unitary channels 
(that is, the channels corresponding to the vertices of the tetrahedron). 
These straightforward channels could be accomplished more efficiently by simply applying the corresponding Pauli operation directly. Nevertheless, due to its general design to accommodate any Pauli channel, the algorithm employs numerous quantum gates even in such scenarios.}
\cpnote{Siento qeu aun falta algo de análisis pero lo dejamos para cuando tengamos mas
figuras y mas inspiracion}
\tbnote{Va}

@@

This theorem implies that when starting from the state $|0\rangle$ 
or any other initial state, the only possible curves of states that can be 
created using a 1PR circuit are of the following form:
\begin{equation}
|\eta(p)\rangle = |c\rangle + e^{is}|a\rangle + e^{-is} |b\rangle,
\label{eq:curve-states}
\end{equation}
with conditions defined by the equations: 
\begin{equation}
\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1,  \quad
\langle a |b\rangle =
\langle a |c\rangle =
\langle b |c\rangle = 0
% , |b\rangle, |c\rangle \; \text{orthogonal states},
%  \text{and} \; a\rangle, |b\rangle, |c\rangle \; \text{orthogonal states},
\label{eq:conditions-vecs}
\end{equation}
where $s = s(p)$ is a function of $p$. 
\cpnote{Es un poco confusa la notacion. Hablas de la norma de a con $|a|$, pero ahi parece
que $a$ es un vector. Sugiero cambiar a $\langle a | a \rangle$ o algo asi sin cargar mucho
la notacion. } \tbnote{Va, concuerdo, listo}
\cpnote{Tambien siento qeu las palabras son un poco raras. Sugiero pasarlo por Chatgpt y 
luego tunearlo (todo este parrafo). Avisame cuando quede eso!} \tbnote{Ya}

Moreover, it is possible to construct a 1PR circuit to generate any given curve of 
states described by \eref{eq:curve-states}. 
One approach to achieve this is by utilizing the circuit 
depicted in \fref{fig:1PR-circuit}, 
with the parametrized rotation $R$ applied to the last qubit controlled by all the 
other qubits. The operators $A$ and $B$ can be defined as follows:
\begin{align*}
&B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N}-1 \rangle + \sqrt{\langle b | b \rangle} |2^{N}-2\rangle + \sqrt{\langle c |c \rangle} |2^N-3\rangle, \\
&A|2^N-1 \rangle = \frac{1}{\sqrt{\langle a | a \rangle}} |a\rangle,\; A|2^{N}-2\rangle = \frac{1}{\sqrt{\langle b | b \rangle}}|b\rangle, \; A|2^{N}-3\rangle = \frac{1}{\sqrt{\langle c | c \rangle}}|c\rangle.
\end{align*}
The rest of the operators $A$ and $B$ can be defined
in any arbitrary manner as long as they are unitary.
By starting from the initial state $|0\rangle$ and 
applying the circuit shown in \fref{fig:1PR-circuit}, straightforward calculations 
lead us to obtain the resulting curve of states described in Equation (\ref{eq:curve-states}).

@@

%Therefore, from this theorem we conclude that
%the kind of curves of states that can be created
%using a 1PR circuit are always of the form
%\begin{align*}
%|b(p)\rangle= e^{is} \vec{a} + e^{-is} \vec{b} + \vec{c},
%\end{align*}
%where $s$ is a function of $p$, $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors and
%$|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2 = 1$.
%%\textbf{Puntos:}
%\begin{itemize}
%\item As said before, to implement a Pauli dynamical map, 
%we need to create the parametrized $2n$-qubit state 
%$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
%\item However, creating this state will in general require many rotations parametrized by $p$. 
%For example, for the case of a Pauli dynamical map on 1 qubit, 
%the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
%In general, to create a parametrized state on $2n$ ancilla qubits will require
%$2n-1$ rotations parametrized by $p$.
%\item How can we reduce the amount of parametrized rotations used?
%\item \textbf{1PR Circuit:} Define an 1PR circuit (a circuit with one parametrized rotation)
%\item \textbf{Theorem about 1PR circuits:} \textit{An 1PR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
%\begin{eqnarray}
%U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
%\end{eqnarray}
%\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
%\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
%aunque se puede y debe achicar bastante.
%\end{itemize}
% }}}

\section{1PR circuit for a Pauli map} % {{{
\label{sec: 1PR circuit for a Pauli map}

We can now use the previous results to conclude directly which Pauli dynamical maps
can be implemented with a 1PR circuit.
Given this condition, the curve of states of \eref{eq: parametrized state}  needed 
to implement the map
has to be constructed with only one parametrized rotation. 
Therefore, the results of the last section imply that the the map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\label{eq:vec}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = |c\rangle +  e^{is} |a\rangle + e^{-is}|b\rangle,
\end{eqnarray}
where $|a\rangle,|b\rangle,|c\rangle$ are orthogonal states  
and $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$.

@@

\begin{figure}
\captionsetup[subfigure]{justification=centering}
\centering
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{images/curvas.png}
   \caption{}
  \label{fig:curves1}
\end{subfigure}%
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{images/curvas-azar.png}
  \caption{}
  \label{fig:curves2}
\end{subfigure}
\caption{{\bf Some Pauli dynamical maps that can be implemented with a 1PR circuit.}
The curves painted in these tetrahedrons
represent Pauli dynamical maps that can be implemented with 1PR circuits.
(a) shows the dynamical maps mentioned in the main 
text, which are: depolarizing (purple), bit flip (blue),
phase flip (green), bit-phase flip (red)
and parabolic (orange).
(b) shows dynamical maps selected at random that can be implemented with 1PR 
circuits.}
\label{fig:curves}
\end{figure}

\begin{itemize}
\item \textbf{Bit flip map:} 
This dynamical map is defined as
\begin{align*}
\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1,
\end{align*}
for $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that 
$|\beta_0(p)|^2= (1-p)^2$, $|\beta_1(p)|^2 = p$, $|\beta_2(p)|^2 = |\beta_3(p)|^2 = 0$.
In particular, if we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{align*}
|\beta(p)\rangle = \sqrt{1-p} |0\rangle +\sqrt{p} |1\rangle.
\end{align*}
This can be rewritten as
\begin{align*}
|\beta(p) \rangle = e^{is}  \left(\frac{1}{2} |0\rangle - \dfrac{i}{2} |1\rangle \right) + e^{-is} \left( \frac{1}{2} |0\rangle + \frac{i}{2} |1\rangle \right),
\end{align*}
with $s= \arcsin(\sqrt{p})$.
Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
and it can be created with a 1PR circuit.
The exact same thing can be done
for the phase flip and bit phase flip dynamical maps by
changing $\sigma_1$ to
$\sigma_3$ and $\sigma_2$ respectively.

\item \textbf{Depolarizing:} This dynamical map is given by
\begin{align*}
\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
\end{align*}
with $p \in [0,1]$. 
Then, taking the $\beta_j$ to be real,
the curve of states needed to create on the ancilla qubits is
\begin{align*}
|\beta(p) \rangle = \sqrt{1-3p/4} |0\rangle + \sqrt{p/4} |1\rangle + \sqrt{p/4} |2 \rangle  + \sqrt{p/4} |3\rangle.
\end{align*}
This state can be rewritten as:
\begin{align*}
|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |0\rangle - \dfrac{i}{2\sqrt{3}} |1\rangle - \dfrac{i}{2\sqrt{3}} |2 \rangle - \dfrac{i}{2\sqrt{3}} |3\rangle \right) \\
& + e^{-is} \left( \dfrac{1}{2} |0\rangle + \dfrac{i}{2\sqrt{3}} |1\rangle + \dfrac{i}{2\sqrt{3}} |2\rangle + \dfrac{i}{2\sqrt{3}} |3 \rangle \right),
\end{align*}
with $s = \arcsin(\sqrt{3p/4})$.
We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
1PR circuit.

@@

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle, |b\rangle, |c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|, |b|, |c|$
such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle,$ $|c'\rangle = |c| |2\rangle$.
\item[3.] Finally, we choose a unitary matrix $V$
and use it to define the states $|a\rangle = V |a'\rangle, |b\rangle = V |b'\rangle, |c\rangle = V |c'\rangle$.
This way, since the primed states are orthogonal and their squared norms add up to one,
so do the unprimed states and therefore 
fulfill the conditions of  \eref{eq:conditions-vecs}. 
\end{itemize}

>>>>

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in \fref{fig: circuit-pauli-1},
which is a special case of \fref{fig: circuit-pauli}
but with all details  explicitly shown.
In said figure, the ancilla state
of \eref{eq: state} can be taken to be
$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
and it is created on the ancilla qubits with the help of three rotations of angles
defined by the following equations:
\begin{align*}
\cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{00} + k_{01}},\\
\tan\left( \dfrac{\theta_1 + \theta_2}{2} \right) &= \sqrt{k_{01}/k_{00}}, \\
\tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{11}/k_{10}}.
\end{align*}

@@

% We took a sample of one-qubit Pauli channels and
% used the ibmq-lima quantum computer that IBM has available~\cite{Qiskit}
% to simulate them. For each of these channels, we used quantum process
% tomography~\cite{Qiskit, Chuang:1996} to obtain the 
% operator $\xi_I$ corresponding to the implementation of the
% circuit.  Then, we compared this operator with the ideal 
% channel $\xi_T$  we
% wanted to implement.

We took a sample of one-qubit Pauli channels
and evaluated their implementation on IBM's
ibmq-lima quantum computer~\cite{Qiskit},
as shown in \fref{fig:fids}. 
For each of the channels sampled, we used 
quantum process tomography~\cite{Qiskit, Chuang:1996} to obtain the 
operator $\xi_I$ corresponding to the implementation of the
circuit in the quantum computer. 
Then, we compared $\xi_I$ with the theoretical 
operator $\xi_T$ of the Pauli channel we wanted to implement.
To see how close the operators $\xi_I$ and 
$\xi_T$ are, we shall use the
diamond distance~\cite{Aharonov,Wilde}, which is defined by
\begin{equation}
||\xi_I - \xi_T ||_{\diamond}  = \max_{\rho} || (\xi_I \otimes I) \rho - (\xi_T \otimes I) \rho ||_1,
\end{equation}
with $I$ the identity map,
$|| \cdot ||_1$ the trace norm and the maximization
done over all density matrices $\rho$.
The calculation of this norm is done using the semi-definite program from reference \cite{Watrous}.
When the two channels are the same,
the diamond distance has a value of $0$, while in the case that the channels
are completely distinguishable, the distance reaches its maximum value of $2$~\cite{Benenti}.
For the analysis done in \fref{fig:fids}, we define a sort of ``diamond fidelity'' as: 
\begin{equation}
f = 1 - \dfrac{1}{2} ||\varepsilon_I - \varepsilon_T ||_{\diamond},
\label{eq:diamond-fid}
\end{equation}
which ranges from $0$, when the channels have a maximum distance, to  $1$,
when they are exactly equal.

Finally, using the representation of Pauli channels in a tetrahedron as
in \eref{eq: conditions-tetrahedron},
we show in \fref{fig:fids} the diamond fidelity defined by \eref{eq:diamond-fid} for the channels
analyzed. 
We can see that channels close to the 
completely depolarizing
channel (that is close to the center of the tetrahedron)
have a high $f$, while those 
close to unitary channels have much lower $f$.
This means that channels closer to the 
completely depolarizing channel are simulated better on the quantum computers.
This is reasonable because quantum computers are prone to errors
that depolarize qubits, which isn't very problematic
when trying to simulate depolarization but it is 
when simulating unitary processes. Moreover, the algorithm of \fref{fig:
circuit-pauli-1} is not optimal for unitary channels (that is, the channels
corresponding to the vertices of the tetrahedron).  These straightforward
channels could be accomplished more efficiently by simply applying the
corresponding Pauli operation directly. Nevertheless, due to its general design
to accommodate any Pauli channel, the algorithm employs numerous quantum gates
even in such scenarios.
\cpnote{Iterar este parrafo cuando estemos cerca del final. Ta un tilin chafa.}

@@

This theorem implies that when starting from the state $|0\rangle$ 
or any other initial state, the only possible curves of states that can be 
created using a 1PR circuit are of the following form:
\begin{equation}
|\eta(p)\rangle = |c\rangle + e^{is}|a\rangle + e^{-is} |b\rangle,
\label{eq:curve-states}
\end{equation}
with conditions defined by the equations: 
\begin{equation}
\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1,  \quad
\langle a |b\rangle =
\langle a |c\rangle =
\langle b |c\rangle = 0
% , |b\rangle, |c\rangle \; \text{orthogonal states},
%  \text{and} \; a\rangle, |b\rangle, |c\rangle \; \text{orthogonal states},
\label{eq:conditions-vecs}
\end{equation}
where $s = s(p)$ is a function of $p$. 
% \cpnote{Es un poco confusa la notacion. Hablas de la norma de a con $|a|$, pero ahi parece
% que $a$ es un vector. Sugiero cambiar a $\langle a | a \rangle$ o algo asi sin cargar mucho
% la notacion. } \tbnote{Va, concuerdo, listo}
% \cpnote{Tambien siento qeu las palabras son un poco raras. Sugiero pasarlo por Chatgpt y 
% luego tunearlo (todo este parrafo). Avisame cuando quede eso!} \tbnote{Ya}

Moreover, it is possible to construct a 1PR circuit to generate any given curve of 
states described by \eref{eq:curve-states}. 
One approach to achieve this is by utilizing the circuit 
depicted in \fref{fig:1PR-circuit}, 
with the parametrized rotation $R$ applied to the last qubit controlled by all the 
other qubits. The operators $A$ and $B$ can be defined as follows:
\begin{align*}
&B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N}-1 \rangle + \sqrt{\langle b | b \rangle} |2^{N}-2\rangle + \sqrt{\langle c |c \rangle} |2^N-3\rangle, \\
&A|2^N-1 \rangle = \frac{1}{\sqrt{\langle a | a \rangle}} |a\rangle,\; A|2^{N}-2\rangle = \frac{1}{\sqrt{\langle b | b \rangle}}|b\rangle, \; A|2^{N}-3\rangle = \frac{1}{\sqrt{\langle c | c \rangle}}|c\rangle.
\end{align*}
The remaining part of the operators $A$ and $B$ can be defined
in any arbitrary manner as long as they are unitary.
By starting from the initial state $|0\rangle$ and 
applying the circuit shown in \fref{fig:1PR-circuit}, straightforward calculations 
lead us to obtain the resulting curve of states described in Equation (\ref{eq:curve-states}).

@@

%Therefore, from this theorem we conclude that
%the kind of curves of states that can be created
%using a 1PR circuit are always of the form
%\begin{align*}
%|b(p)\rangle= e^{is} \vec{a} + e^{-is} \vec{b} + \vec{c},
%\end{align*}
%where $s$ is a function of $p$, $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors and
%$|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2 = 1$.
%%\textbf{Puntos:}
%\begin{itemize}
%\item As said before, to implement a Pauli dynamical map, 
%we need to create the parametrized $2n$-qubit state 
%$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
%\item However, creating this state will in general require many rotations parametrized by $p$. 
%For example, for the case of a Pauli dynamical map on 1 qubit, 
%the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
%In general, to create a parametrized state on $2n$ ancilla qubits will require
%$2n-1$ rotations parametrized by $p$.
%\item How can we reduce the amount of parametrized rotations used?
%\item \textbf{1PR Circuit:} Define an 1PR circuit (a circuit with one parametrized rotation)
%\item \textbf{Theorem about 1PR circuits:} \textit{An 1PR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
%\begin{eqnarray}
%U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
%\end{eqnarray}
%\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
%\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
%aunque se puede y debe achicar bastante.
%\end{itemize}
% }}}
\section{1PR circuit for a Pauli map} % {{{
\label{sec: 1PR circuit for a Pauli map}

We can now use the previous results to conclude directly which Pauli dynamical maps
can be implemented with a 1PR circuit.
Given this condition \cpnote{which?}, the curve of states of \eref{eq: parametrized state}  needed 
to implement the map
has to be constructed with only one parametrized rotation. 
Therefore, the results of the last section imply that the the map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\label{eq:vec}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = |c\rangle +  e^{is} |a\rangle + e^{-is}|b\rangle,
\end{eqnarray}
where $|a\rangle,|b\rangle,|c\rangle$ are orthogonal states  
and $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$ \cpnote{redundante, refierete mejor a la ecuacion anterior, a la 24 pues. Ahora, también creo qeu la pedendencia
con $p$ no está clara del lado derecho. Quizpa si se escribe $s(p)$ en vez de 
$s$ es mejor, pero piensale tambien . }.

@@

\begin{figure} % {{{
\captionsetup[subfigure]{justification=centering}
\centering
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{images/curvas.png}
   \caption{}
  \label{fig:curves1}
\end{subfigure}%
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{images/curvas-azar.png}
  \caption{}
  \label{fig:curves2}
\end{subfigure}
\caption{{\bf Some Pauli dynamical maps that can be implemented with a 1PR circuit.}
The curves painted in these tetrahedrons
represent Pauli dynamical maps that can be implemented with 1PR circuits.
(a) shows the dynamical maps mentioned in the main 
text, which are: depolarizing (purple), bit flip (blue),
phase flip (green), bit-phase flip (red)
and parabolic (orange).
(b) shows dynamical maps selected at random that can be implemented with 1PR 
circuits.}
\label{fig:curves}
\end{figure} % }}}

\begin{itemize}
\item \textbf{Bit flip map:} 
\cpnote{Aca solo usas dos niveles, pero el caso general requiere 2 qubits. Ahora, si solo 
se requiere un qubit, pues está chido pero toca decirlo. Quizá dejarlo como un ultimo ejemplo. 
Toca citar acá tambien el trabajo de los brasileños... a ver si lo encuentro, Andrea 
Valdez me va a pasar la cita. De hecho pordemos leer el articulo para inspiracion y citar}
This dynamical map is defined as
\begin{align*}
\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1,
\end{align*}
for $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that 
$|\beta_0(p)|^2= (1-p)^2$, $|\beta_1(p)|^2 = p$, $|\beta_2(p)|^2 = |\beta_3(p)|^2 = 0$.
In particular, if we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{align*}
|\beta(p)\rangle = \sqrt{1-p} |0\rangle +\sqrt{p} |1\rangle.
\end{align*}
This can be rewritten as
\begin{align*}
|\beta(p) \rangle = e^{is}  \left(\frac{1}{2} |0\rangle - \dfrac{i}{2} |1\rangle \right) + e^{-is} \left( \frac{1}{2} |0\rangle + \frac{i}{2} |1\rangle \right),
\end{align*}
with $s= \arcsin(\sqrt{p})$\cpnote{Que tal si lo dejamos como $\sin s= \sqrt{p}$? Si estas de 
acuerdo igual cambia los siguientes}.
Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
and it can be created with a 1PR circuit.
The exact same thing can be done
for the phase flip and bit phase flip dynamical maps by
changing $\sigma_1$ to
$\sigma_3$ and $\sigma_2$ respectively.

\item \textbf{Depolarizing:} This dynamical map is given by
\begin{align*}
\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
\end{align*}
with $p \in [0,1]$. 
Then, taking the $\beta_j$ to be real,
the curve of states needed to create on the ancilla qubits is
\begin{align*}
|\beta(p) \rangle = \sqrt{1-3p/4} |0\rangle + \sqrt{p/4} |1\rangle + \sqrt{p/4} |2 \rangle  + \sqrt{p/4} |3\rangle.
\end{align*}
This state can be rewritten as:
\begin{align*}
|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |0\rangle - \dfrac{i}{2\sqrt{3}} |1\rangle - \dfrac{i}{2\sqrt{3}} |2 \rangle - \dfrac{i}{2\sqrt{3}} |3\rangle \right) \\
& + e^{-is} \left( \dfrac{1}{2} |0\rangle + \dfrac{i}{2\sqrt{3}} |1\rangle + \dfrac{i}{2\sqrt{3}} |2\rangle + \dfrac{i}{2\sqrt{3}} |3 \rangle \right),
\end{align*}
with $s = \arcsin(\sqrt{3p/4})$.
We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
1PR circuit.
\cpnote{De nuevo, quizá aca convenga tener notacion de qubits y no de sistemas de 4 niveles}

@@

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle, |b\rangle, |c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|, |b|, |c|$
such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle,$ $|c'\rangle = |c| |2\rangle$.
\item[3.] Finally, we choose a unitary matrix $V$ \cpnote{Esta supongo qeu 
la escoges aleatoriamente, y que la tomas por ahi del CUE. Lo platicamos y metemos 
los detalles. }
and use it to define the states $|a\rangle = V |a'\rangle, |b\rangle = V |b'\rangle, |c\rangle = V |c'\rangle$.
This way, since the primed states are orthogonal and their squared norms add up to one,
so do the unprimed states and therefore 
fulfill the conditions of  \eref{eq:conditions-vecs}. 
\end{itemize}
